Trauma treatment delay

### 2023-10-18 lab-book.Rmd
set categories
Heaps of code

>>>>

The categorical factors

-   sex- Gender

-   survival after 30 days- res_survival

-   highest hospital care level- host_care_level

-   GCS- ed_gcs_sum

-   respiratory rate- ed_rr_value

-   systolic blood pressure- ed_sbp_value

-   working hours

-   weekend

-   time from arrival at the hospital until first computed tomography
    (CT)- dt_ed_first_ct

-   if the patient was intubated- ed_intubated eller pre_intubated

We also included the continuous factors

-   age- pt_age_yrs

-   ISS- ISS

New.subset\$dt_ed_first_ct \<- as.factor(New.subset\$dt_ed_first_ct)
